\documentclass{article}[10]
\usepackage{times}
\oddsidemargin 0.0in
\evensidemargin 0.0in
\textwidth 6.5in
\headheight 0.0in
\topmargin 0.0in
\textheight 9.0in
\begin{document}
\section*{Resume for Richard John NEISH}
Born Kingston Jamaica 11$^{th}$ March, 1974\\
{\bf Contact Address}\\
7 Glenwood Avenue,\\
London, NW9 7PL\\
UK\\
Mobile: 07729 167 059 \hspace{0.3 in} Email: richardneish@email.com
\subsection*{Skills}
Programming Languages: Java, C/C++, SQL, Perl, Visual Basic, UNIX shell script \\
Operating Systems: GNU/Linux (esp Red Hat), Sun Solaris, SCO OpenServer 5, Microsoft Windows NT/2000 \\
Tools / Applications: Jakarta Tomcat, Sun Forte, Jakarta Velocity, Apache, Informix, Samba, CVS, Oracle, Postgres, Emacs, LaTex, Microsoft Visual Studio 6, Macromedia Dreamweaver 4 \\
Other Technologies / Keywords: TCP/IP, DNS, SMTP, JDBC, NFS, SMB, NIS, LDAP, HTML, CGI \\
Other Skills: Familiar with PC and Sun workstation hardware, Jamaican Private Pilot's Licence.
\subsection*{Goals}
To identify and apply {\em appropriate} technology for solving real-world problems.  Buzzwords, hype and marketing aside, to select or develop systems based on the needs of the business and the technical merits of the solution.
\subsection*{Experience}
\noindent September 1999 - June 2002\\
Partner and Senior Developer,\\
RMP \& Associates,\\
Kingston, Jamaica

As a director for this small consulting and systems development firm, worked in a wide variety of roles including systems design and implementation, programming, network optimisation and security and database and network administration.  Projects completed include:
\begin{itemize}
\item Remotely administer internet server systems, including a Linux web server serving over 200GB of traffic per month and a web-based email system with 6000+ users.
\item Designed and developed a Java-based payroll system.  The system is completely data-driven, storing payroll formulae as first-class data items, allowing the system to be tailored to any system of deductions or taxes.  The system is implemented in Java2 with an Informix RDMBS backend and is currently in production use on both Windows 2000 Server and RedHat Linux systems.
\item WAN Network security and optimization for a Jamaican bank comprising 28 branch offices and 2 data centres connected by a TCP/IP network running over leased line.  Collaborated with bank IT staff on system documentation and security and reported on same to senior management.
\item Designed and implemented a Perl-based CGI system for online publishing for a local newspaper.  Migrated an existing offline system to a database-backed, template-driven publishing system, including mass email publishing and archive searching.  Later additions to this project, including the archive search interface, were implemented using Java Servlets.
\item Designed and developed front-end system for interfacing with Informix 4GL legacy code.  Interfaces include an Interactive Voice Response system and a Java servlet-based web application.
\end{itemize}

\noindent September - December 2000 and January - May 2002\\
Lecturer, Department of Mathematics and Computer Science,
\\University of the West Indies,\\
Kingston, Jamaica

Developed and presented a course entitled ``Advanced Operating Systems''.  This course formed one component of the universities MSc Programme in Computer Science.\\

\noindent September 1997 - August 1999\\
UNIX Systems Administrator,\\
Digital Systems Processing / Image Formation and Processing groups,\\
University of Illinois, USA.

Maintained a laboratory and network comprised of 50+ UNIX workstations and servers.  Systems included Solaris, SunOS and HP/UX servers and workstations in addition to PC and Macintosh workstations and printers, connected by an Ethernet running TCP/IP and AppleTalk.  I am responsible for installing and configuring software packages and services, including HTTPD, NIS, NFS, TeX, X Window System, Matlab, and others.\\

\noindent June 1998 - August 1998\\
Data Management Specialist,\\
Business Link LCP,\\
London, England

Transitioned a large database application from Novell Netware to Windows NT and upgraded from Oracle 5 to Oracle 7.  Rolled out upgraded system to 100+ clients in three offices, with zero lost work or data.  Converted all reports and queries to new system and set up training facilities for staff.\\

\noindent May 1995 - January 1997\\
Senior Programmer,\\
Advanced Integrated Systems,\\
Kingston, Jamaica

Major projects completed include a proposed National Identification Card system for the Government of Jamaica, a general purpose ID production system and a printing subsystem for the Registrar of Births, Deaths and Marriages, Government of Jamaica.  I developed front ends for Informix and SQL Server databases, in Visual Basic and using HTML and CGI scripts.\\

\noindent May-June 1995 and May-June 1996\\
Lecturer,\\
Department of Management Studies, University of the West Indies,\\
Kingston, Jamaica

I developed and presented a 4 week course entitled Introduction to Windows Programming using Visual Basic.  The course was presented as part of the University's C-MIS programme.

\subsection*{Education}
\noindent September 1997 - August 1999\\
University of Illinois at Urbana-Champaign, Urbana, Illinois, USA\\
Completed MSc in Computer Science August 1999\\

\noindent September 1992 - June 1995\\
University of the West Indies, Mona Campus, Kingston, Jamaica\\
Completed BSc in Computer Science and Electronics June 1995\\

\noindent September 1985 - June 1992\\
Campion College High School, Kingston, Jamaica\\
Completed 9 'O' Levels July 1990, 4 'A' Levels July 1992

\subsection*{Hobbies}
Sailing, Hiking, Flying
\end{document}
